Comparing variations in sediment transport capacity between subglacial and subaerial systems

### 2023-03-20 theory.tex
Updates from Overleaf

  Here, it is assumed that the water is transported through subglacial channels \citep[Figure~\ref{fig:cartoon}; ][]{rothlisberger1972}, and that the channel  and geometry will respond to a representative water discharge over a certain time period $Q_{w}^*$, using the Darcy-Weisbach formulation for water-flow through a pipe  \citep[e.g.][]{rothlisberger1972,clarke2003,werder2013}.
  Thus, the hydraulic diameter of the subglacial channel, $D_h$, responds to a representative water discharge, $Q_{w}^*$, and a representative gradient of the hydraulic potential, $\Psi^*$ such that:
  \begin{linenomath*}
    \begin{equation}
      \label{eq:DW}
      D_h = \big(s\, f_r\,\rho_w\, \frac{Q_w^{*\,2}}{\Psi^*}\big)^{\frac{1}{5}}~~.
    \end{equation}
  \end{linenomath*}
  % 
  The representative hydraulic gradient is based upon the pressurized flow in Equation~\ref{eq:DW},
  \begin{equation}
    \label{eq:psi}
    \Psi^*= f_f \,  \rho_i \, g (\frac{\partial  z_{sg}}{\partial x} - \frac{\partial z_c}{\partial x}) +  \rho_i \, g \, \frac{\partial z_c}{\partial x},
  \end{equation}
  % 
  \noindent
  where, $f_f$ is the flotation fraction, $\rho_i$ is density of ice $\frac{\partial z_{sg}}{\partial x}$ is the surface slope of the glacier and $\frac{\partial z_c}{\partial x}$ is the glacier bed slope.

@@

  In the subaerial system, the water is not pressurized, so only the bed slope, $\frac{\partial z_c}{\partial x}$, is needed in Equation~\ref{eq:DW_tau}. The friction factor, $f_f$, and channel shape factor, $k$, are assigned such that they produce reasonable values for water velocity and channel width  (Section~\ref{sect:fluv}).

@@

  \section{Discussion}
  \subsection{Assumptions}

  In R-channel formulations, peaks in the hydrograph could cause additional opening of the conduit due to pressure melt, thus causing a decrease in velocity compared to the results here \citep{rothlisberger1972}.
  A similar effect could occur with creep closure of the subglacial channel at the hydrograph minima.
  Additionally, at high water pressures, glacier uplift and bed separation \citep{andrews2014} might modify the width of the subglacial channel.

@@

>>>>

  Here, it is assumed that the water is transported through subglacial channels \citep[Figure~\ref{fig:cartoon}; ][]{rothlisberger1972}, and that the channel  geometry will respond to a representative water discharge over a certain time period $Q_{w}^*$, using the Darcy-Weisbach formulation for water-flow through a pipe  \citep[e.g.][]{rothlisberger1972,clarke2003,werder2013}.
  Thus, the hydraulic diameter of the subglacial channel, $D_h$, responds to a representative water discharge, $Q_{w}^*$, and a representative gradient of the hydraulic potential, $\Psi^*$ such that:
  \begin{linenomath*}
    \begin{equation}
      \label{eq:DW}
      D_h = \big(s\, f_r\,\rho_w\, \frac{Q_w^{*\,2}}{\Psi^*}\big)^{\frac{1}{5}}~~.
    \end{equation}
  \end{linenomath*}
  % 
  The representative hydraulic gradient is based upon the pressurized flow in Equation~\ref{eq:DW},
  \begin{equation}
    \label{eq:psi}
    \Psi^*= f_f \,  \rho_i \, g (\frac{\partial  z_{sg}}{\partial x} - \frac{\partial z_c}{\partial x}) +  \rho_i \, g \, \frac{\partial z_c}{\partial x},
  \end{equation}
  % 
  \noindent
  where, $f_f$ is the flotation fraction, $\rho_i$ is density of ice $\frac{\partial z_{sg}}{\partial x}$ is the surface slope of the glacier and $\frac{\partial z_c}{\partial x}$ is the glacier bed slope.

@@

  In the subaerial system,  only the bed slope, $\frac{\partial z_c}{\partial x}$, is needed in Equation~\ref{eq:DW_tau}. The friction factor, $f_f$, and channel shape factor, $k$, are assigned such that they produce reasonable values for water velocity and channel width  (Section~\ref{sect:fluv}).

@@

  \section{Discussion}

@@

  \subsection{Assumptions}
